HUME: Human UCCA-Based Evaluation of Machine Translation

### 2016-03-18 paper/main.tex
squashing space

These translation systems were used to translate texts derived from both NHS 24\footnote{\url{http://www.nhs24.com/}} and Cochrane\footnote{\url{http://www.cochrane.org/}} into the four languages. The first organisation is a public body providing healthcare and health-service related information in Scotland, whereas the second is an international NGO which 
provides independent systematic reviews on health-related research. From NHS 24, we selected the segments from their
``Health A-Z'' which is part of the NHS Inform website, and the Cochrane texts come from their plain language summaries
and abstracts.

@@

For the annotation of the MT output, we recruited two annotators for each of German, Romanian
and Polish and one main annotator for Czech.
%In order to allow us to calculate
For IAA also for
the Czech, we recruited several further annotators to work on a small number of 
sentences each. We treat these further annotators as one annotator, giving us two annotators
for each language pair.
The annotators were all native  speakers of the respective target languages and fluent in English.

@@

}
\end{tabular}
\caption{Inter-annotator Agreement (Kappa) versus sentence length, separately for
structural and atomic nodes. The numbers are the node counts in each bin. }
\label{fig:iaalength}
\end{figure}

@@

This focus on verbal predicates has a number of unfortunate consequences. We show an example below:

@@

There are however a number of other serious consequences on focussing on verbal
predicates. We conducted an analysis of the English UCCA Wikipedia
corpus, comprising
of 5324 sentences,
in order to assess the impact of the following problems: 
\\
\begin{inparadesc}
\item[Copula clauses] are treated in HMEANT simply as instances of the main verb ``be'', which
generally does not convey the meaning of these clauses. They appear in 21.7\% of the sentences,
according to conservative estimates that only considers non-auxilliary instances of ``be''.
\\
\item[Nominative argument structures,] which are completely ignored under HMEANT are in fact highly
pervasive, appearing in 48.7\% of the sentences.
\\
\item[Linkers] expressing an inter-relation between
clauses (mainly discourse markers and coordinating conjunctions) appear in 56\% of the
sentences\footnote{Argument structures and linkers are explicitly marked in UCCA. We identified non-auxilliary instances of ``be'' and nouns using the NLTK standard tagger. Nominative argument structures are here defined as Scenes whose main relation is headed by a noun.}.
\end{inparadesc}

@@

In HMEANT, the alignment between the (reference and translation) structures is a key
part of the manual annotation. If the alignment cannot be created, the 
translation is heavily penalized.
Previous experiments with HMEANT
\parcite{bojar:wu:ssst:2012,chuchunkov-tarelkin-galinskaya:2014:SSST-8} have
suggested that sometimes, the structures of the reference and of an accurate translation
still diverge, for instance due to a different
interpretation of a PP-attachment, or the verb having an additional modifier in
%suggested that sometimes, the structures of the reference and candidate
%translations diverge without any good reason, for instance due to a different
%interpretation of a PP-attachment, the verb can have one additional modifier in
one of the structures. It would be desirable to allow updates to the structural
annotations at the alignment stage,
to avoid unduly penalization due to such spurious divergences.
%annotations also at the alignment stage
%to avoid unduly penalization due to such a spurious divergence.
The same issue was seen by HMEANT authors themselves
\parcite{lo:wu:reliability:2014}:
the 
inter-annotator agreement on SRL dropped from 90\% to 61\% 
when the two aligned structures were from two different annotators.

>>>>

These translation systems were used to translate texts derived from both NHS
24\footnote{\url{http://www.nhs24.com/}} and
Cochrane\footnote{\url{http://www.cochrane.org/}} into the four languages.
NHS~24 is a public body providing healthcare and health-service
related information in Scotland, Cochrane is an international NGO
which 
provides independent systematic reviews on health-related research. From NHS 24, we selected the segments from their
``Health A-Z'' which is part of the NHS Inform website, and the Cochrane texts come from their plain language summaries
and abstracts.

@@

For the annotation of the MT output, we recruited two annotators for each of German, Romanian
and Polish and one main annotator for Czech.
%In order to allow us to calculate
For IAA also for
Czech, several further annotators worked on a small number of 
sentences each. We treat these further annotators as one annotator, giving us two annotators
for each language pair.
The annotators were all native  speakers of the respective target languages and fluent in English.

@@

}
\end{tabular}
\caption{Kappa versus sentence length, separately for
structural and atomic nodes. The numbers are the node counts in each bin. }
\label{fig:iaalength}
\end{figure}

@@

%This focus on verbal predicates has a number of unfortunate consequences. We show an example below:
Consider the example:

% \noindent
% \begin{inparadesc}
% \item[Source ] a coronary angioplasty may not be technically possible \\
% \item[Transl.] eine koronare Angioplastie kann nicht technisch m{\"o}glich \\
% \item[Gloss ]  a coronary angioplasty can not technically possible \\
% \end{inparadesc}

@@

There are however a number of other serious consequences on focussing on verbal
predicates. We conducted an analysis of the English UCCA Wikipedia
corpus (5324 sentences)
in order to assess the impact of the following problems: 
\\
\begin{inparadesc}
\item[Copula clauses] are treated in HMEANT simply as instances of the main verb ``be'', which
generally does not convey the meaning of these clauses. They appear in 21.7\% of the sentences,
according to conservative estimates that only considers non-auxilliary instances of ``be''.
\\
\item[Nominal argument structures,] which are completely ignored under HMEANT, are in fact highly
pervasive, appearing in 48.7\% of the sentences.
\\
\item[Linkers] expressing an inter-relation between
clauses (mainly discourse markers and coordinating conjunctions) appear in 56\% of the
sentences\footnote{Argument structures and linkers are explicitly marked in UCCA. We identified non-auxilliary instances of ``be'' and nouns using the NLTK standard tagger. Nominative argument structures are here defined as Scenes whose main relation is headed by a noun.}.
\end{inparadesc}

@@

In HMEANT, the alignment between the (reference and translation) structures is a key
part of the manual annotation. If the alignment cannot be created, the 
translation is heavily penalized.
Previous experiments with HMEANT
\parcite{bojar:wu:ssst:2012,chuchunkov-tarelkin-galinskaya:2014:SSST-8} have
suggested that sometimes, the structures of the reference and of an accurate translation
still diverge, for instance due to a different
interpretation of a PP-attachment, or the verb having an additional modifier in
%suggested that sometimes, the structures of the reference and candidate
%translations diverge without any good reason, for instance due to a different
%interpretation of a PP-attachment, the verb can have one additional modifier in
one of the structures. It would be desirable to allow updates to the structural
annotations at the alignment stage,
to avoid unduly penalization due to such spurious divergences.
%annotations also at the alignment stage
%to avoid unduly penalization due to such a spurious divergence.
The same issue was seen by HMEANT authors themselves
\parcite{lo:wu:reliability:2014}:
the 
IAA on SRL dropped from 90\% to 61\% 
when the two aligned structures were from two different annotators.
